---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse   = TRUE,
  warning    = FALSE,
  message    = FALSE,
  comment    = "#>",
  fig.path   = "man/figures/",
  fig.retina = 3
)
```

# jph: Miscellaneous R Functions

<!-- badges: start -->

<!-- badges: end -->

## Installation

You can install this package from [GitHub](https://github.com/jhelvy/jph):

```r
# install.packages("remotes")
remotes::install_github("jhelvy/jph")
```

Load the package with:

```{r, eval=FALSE}
library(jph)
```

## Contents

This package contains the following functions:

* `ci()`: Get confidence intervals for a vector of numbers or for every column in a data frame of numeric columns.
* `cs()`: Returns a vector of character strings from list of unquoted names (copied directly from the Hmisc package).
* `ggtornado()`: Creates a "tornado" plot using the [{ggplot2}](https://ggplot2.tidyverse.org/) package.
* `jColors()`: A list of nice color palettes.
* `jTheme()`: A custom theme for making plots in ggplot2.
* `logit_probs()`: Computes logit fraction given a set of coefficients and alternatives.
* `print_names()`: Prints the names of a data frame in a column so they're easy to copy.
* `quantile_speed()`: A faster version of `quantile()`, taken from [this gist](https://gist.github.com/sikli/f1775feb9736073cefee97ec81f6b193)
* `read_zip()`: Downloads a zipped file from the web and return the local paths to each file.
* `rep_df()`: Repeats a data frame `n` times.
* `source_dir()`: Source all R files in a given directory.
* `vector_code()`: Prints the code to concatenate a vector of strings.

To view more details of any of the functions, run `?functionName()` in R, replacing 'functionName' with the name of the function.

## Author, Version, and License Information

- Author: *John Paul Helveston* https://www.jhelvy.com/
- Date First Written: *Saturday, March 18, 2017* in the Cathedral of Learning in Pittsburgh, PA
- License: [MIT](https://github.com/jhelvy/jph/blob/master/LICENSE.md)

## Citation Information

If you use this package for in a publication, I would greatly appreciate it if you cited it - you can get the citation by typing `citation("jph")` into R:

```{r}
citation("jph")
```
