---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse   = TRUE,
  warning    = FALSE,
  message    = FALSE,
  comment    = "#>",
  fig.path   = "man/figures/",
  fig.retina = 3
)
```

# jph: Miscellaneous R Functions

## Installation

You can install this package from [GitHub](https://github.com/jhelvy/jph):

```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("jhelvy/jph")
```

Load the package with:

```{r, eval=FALSE}
library(jph)
```

## Contents

See the [Reference](https://jhelvy.github.io/jph/reference/index.html) documentation page for descriptions and details of all package functions.

## Author, Version, and License Information

- Author: *John Paul Helveston* https://www.jhelvy.com/
- Date First Written: *Saturday, March 18, 2017* in the Cathedral of Learning in Pittsburgh, PA
- License: [MIT](https://github.com/jhelvy/jph/blob/master/LICENSE.md)

## Citation Information

If you use this package for in a publication, I would greatly appreciate it if you cited it - you can get the citation by typing `citation("jph")` into R:

```{r}
citation("jph")
```
